Future Virtual Particle Method for Pedestrian Navigation

### 2015-02-05 doc/informe/paper.tex

%% LyX 2.0.6 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english]{article}
\usepackage[latin9]{inputenc}
\usepackage[a4paper]{geometry}
\geometry{verbose,tmargin=1in,bmargin=1in,headheight=1in,headsep=1in}
\usepackage{float}
\usepackage{textcomp}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}

@@

The Social Force is a model presented by Helbing \cite{key-0,key-1}
in several publications. This paper will focus on the latest version
of the model \cite{key-1}. In his model, each pedestrian $i$ occupies
a circular area of redius $r_{i}$ and is governed by thee forces.
\[
\vec{F_{i}}=\vec{F_{D_{i}}}+\vec{F_{C}}+\vec{F_{s}}
\]

@@

While this model doesn't present a very real behaviour for pedestrians,
it worked as a starting point for numerous projects.

@@

The main effects that govern the motion of a pedestrian are the same
as Helbin's: 
\begin{enumerate}
\item The pedestrian wants to reach his goal in the shortest possible path. 
\item The pedestrian's movement is influenced by other pedestrians. Depending
on the distance between the two of them and the predicted trajectory,
the pedestrian will feel the need to change his route to be able to
avoid the other pedestrians. It is because of this effect that pedestrians
will need to recalculate their route as new pedestrians get closer
to them. 
\item Movement speed will be influenced by needs. 
\end{enumerate}

@@

Represents the space that this pedestrian occupies. Circle's radio
is generated randomly to represent different types of pedestrians.
The range of values is distributed uniformly in $[0.25,0.29]$$[cm]$.

@@

Represented by a static area. When it is touched by a pedestrian,
it is considered as accomplished. Multiple objectives can by defined
in a list, in this case, each of them must be reached in order.

@@

Represents the speed the pedestrian would walk if he was alone. Varies
with a uniform distribution between $[1.2,1.4]\,[m/s]$.

@@

Figure \ref{fig:Pedestrian-top-view} shows a pedestrian geometrical
definition:

\begin{figure}[H]
\centering{}\includegraphics[scale=0.5]{pics/pedestrian-top}\caption{\label{fig:Pedestrian-top-view}Pedestrian top view}
\end{figure}

\vspace{1cm}
 Pedestrians will be named after a letter (i.e: $i$ or $j$) and
the same letter with a apostrophe will represent it's FVP (i.e: $i'$
or $j'$)\\

Figure \ref{fig:Pedestrian-vectors} shows all the vectorial definition
that will be used:

\begin{figure}[H]
\centering{}\includegraphics[scale=0.5]{pics/geometry}\caption{\label{fig:Pedestrian-vectors}Vectorial definitions}
\end{figure}

@@

\subsubsection{Forces}
\begin{itemize}
\item Dynamic of the FVP

@@

To model this situations, two types of forces act over the FVP:
\begin{itemize}
\item Internal force \\
 \\
 This force will guide the pedestrian on the shortest path $\mathbf{ox_{i}}$
and minimize the time needed to reach the long term goal. This force
is modeled using two springs: \\
 \iffalse This forces will try to keep the FVP aligned with $\mathbf{o}$
and at the same time, keep the FVP at $RD$ from the pedestrian.

This (first) spring will regulate the velocity that will be calculated
on a posterior step at which the pedestrian $i$ will advance. ...
which pushes the FVP towards its desired length. At the same time,
a force pushing the FVP towards his original alingment, defined

\fi

The first spring starts on $x_{i'}$ and ends on the point at distance
$RD$ on vector $\mathbf{x_{i}o}$ with a spring constant $K_{1}$.
This spring represents how much the pedestrian wants to reach his
target. A larger spring constant will force a more straight path,
but possible with more collisions on its way. In order to avoid an
oscillatory movement (i.e: with a single pedestrian), a damping $\gamma$
was added to this spring.

The second spring starts on $x_{i}$, ends on $x_{i}'$ and has a
steady distance of $RD$ with a spring constant $K_{s}(\theta)$ where
$\theta$ is the angle between $\mathbf{u}$ and $\mathbf{r}$. With
this spring the FVP will tend to always be at $RD$ distance from
the pedestrian. Because a pedestrian always tries to reach his goal
in the shortest possible path (hypothesis 1), if it has to take a
big detour of his ideal path, it will try to reduce his velocity drastically
in order to avoid making a long travel. To recreate this, the spring
constant has to be dependant of the deviation angle. 
\[
K_{s}(\theta)=\frac{K_{2}}{\theta}
\]

@@

\begin{equation}
\iffalse F_{s}(r,\theta)=K_{s}(\theta)\frac{\vec{ii'}}{\mid\vec{ii'}\mid}(r_{max}-r_{ii'})\fi F_{internal}(i)=K_{1}*(|r|-RD)+K_{2}(\theta_{i})+K_{2}(\theta_{i})*(???)
\end{equation}

@@

The pedestrian always wants to move in the direction his FVP is pointing
and its magnitude is defined as $F_{d}$ or desire force:

\[
F_{desire_{i}}=m_{i}\frac{\frac{|\vec{ii'}|}{|\vec{r}_{max}|}\vec{e_{i}}-\vec{v}_{i}}{\tau}
\]

>>>>

%% LyX 2.0.6 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english]{article}
\usepackage[latin9]{inputenc}
\usepackage[a4paper]{geometry}
\geometry{verbose,tmargin=1in,bmargin=1in,headheight=1in,headsep=1in}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}

@@

The Social Force is a model presented by Helbing \cite{key-0,key-1}
in several publications. This paper will focus on the latest version
of the model \cite{key-1}. In his model, each pedestrian $i$ occupies
a circular area of radius $r_{i}$ and is governed by thee forces.
\[
\vec{F_{i}}=\vec{F_{D_{i}}}+\vec{F_{S_{i}}}+\vec{F_{G_{i}}}
\]

@@

@@

The main effects that govern the motion of a pedestrian are the same
as Helbin's \cite{key-0,key-1}: 
\begin{enumerate}
\item The pedestrian wants to reach his goal in the shortest possible path. 
\item The pedestrian's movement is influenced by other pedestrians. Depending
on the distance between the two of them and the predicted trajectory,
the pedestrian feels the need to change his route to be able to avoid
the other pedestrians. It is because of this effect that pedestrians
will need to recalculate their route as new pedestrians get closer
to them. 
\item Movement speed will be influenced by the presence of other pedestrians
and obstacles.
\end{enumerate}

@@

Represents the personal space of a pedetrian. The value of the radio
is generated randomly for each pedestrian. The range of values is
distributed uniformly in $[0.25,0.29]$$[cm]$.

@@

Represented by a static area. When it is touched by a pedestrian,
it is considered as accomplished. Multiple objectives may by defined
in a list, in this case, each of them must be reached in order.

@@

This is the speed the pedestrian would walk if he/she was alone. This
represents the constant $v_{di}$ in ecuation \ref{eq:driving-force}.
It takes a different value for each pedestrian. Varies with a uniform
distribution between $[1.2,1.4]\,[m/s]$.

@@

\begin{figure}[H]
\centering{}\includegraphics[scale=0.5]{pics/pedestrian-top}\caption{\label{fig:pedestrian-geometry}Pedestrian geometry}
\end{figure}

For the sake of clarity. A single pedestrian will be named after a
letter (i.e: $i$ or $j$) and the same letter with a apostrophe will
represent it's FVP (i.e: $i'$ or $j'$)\\

Figure \ref{fig:pedestrian-vectors} shows all the vectorial definition
that will be used:

\begin{figure}[H]
\centering{}\includegraphics[scale=0.5]{pics/geometry}\caption{\label{fig:pedestrian-vectors}Vectorial definitions}
\end{figure}

@@

\subsubsection{Calculatin of forces}
\begin{itemize}
\item Dynamic of the FVP

@@

To model this situations, two types of forces act over the FVP:
\begin{itemize}
\item Internal force \\
 \\
 This force will guide the pedestrian on the shortest path $\mathbf{ox_{i}}$.
This force is modeled using two springs:

The first spring starts on $x_{i}$, ends on $x_{i}'$ and has a steady
distance of $RD$ with a spring constant $K_{s}(\theta)$ where $\theta$
is the angle between $\mathbf{u}$ and $\mathbf{r}$. With this spring
the FVP will tend to always be at $RD$ distance from the pedestrian.
Because a pedestrian always tries to reach his goal in the shortest
possible path (hypothesis 1), if it has to take a big detour of his
ideal path, it will try to reduce his velocity drastically in order
to avoid making a long travel. To recreate this, the spring constant
has to be dependant of the deviation angle. 
\[
K_{s}(\theta)=\frac{K_{2}}{\theta}
\]

The second spring starts on $x_{i'}$ and ends on the point at distance
$RD$ on vector $\mathbf{x_{i}o}$ with a spring constant $K_{1}$.
This spring represents how much the pedestrian wants to reach his
target. A larger spring constant will force a more straight path,
but possible with more collisions on its way. In order to avoid an
oscillatory movement (i.e: with a single pedestrian), a damping $\gamma$
was added to this spring.\\

@@

\begin{equation}
F_{internal}(i)=K_{1}*(|r|-RD)+K_{2}(\theta_{i})+K_{2}(\theta_{i})*(???)
\end{equation}

$\iffalse F_{s}(r,\theta)=K_{s}(\theta)\frac{\vec{ii'}}{\mid\vec{ii'}\mid}(r_{max}-r_{ii'})\fi$

@@

The pedestrian always wants to move in the direction his FVP is pointing
and its magnitude is defined as $F_{d}$ or driving force:

\[
\vec{F}_{desire_{i}}=m_{i}\frac{\frac{|\vec{ii'}|}{|\vec{r}_{max}|}\vec{e_{i}}-\vec{v}_{i}}{\tau}
\]
